English-Chinese Translation Machine Based on Sequence to Sequence Network

### 2022-11-22 ML2/paper.tex
11-22

\HRule \\[1cm]
{ \huge \bfseries The Experiment I Report of \textit{Machine Learning} }\\[0.6cm] % Title of your document
\HRule \\[2cm]
%----------------------------------------------------------------------------------------
%	HEADING SECTIONS
%----------------------------------------------------------------------------------------

@@

% Define document title and author
	\title{Face Detection Based on Neural Network}
	\author{Jianqiao Hu \thanks{autor's email: 202221045886@mail.scut.edu.cn}}
	\maketitle

@@

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{F}{ace} detection is a important research hotspot in computer vision research field. Nowadays, it plays a significant role in auto-driving and smart home IoT system. Some methods like \cite{ZHAN201619} used convolutional neural network (CNN). This experience use method raised by \cite{8080244} to detection faces in photos.

% Main Part
\section{Methods and Theory}
In \cite{8080244}, it propose Multi-task convolutional neural network

\section{Experiments}
\subsection{Dataset}
Test dataset includes handurds of photos and all of them has at least one people.

@@

		\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/13869.jpg}
		% Create a subtitle for the figure.
		\caption{result with a person}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13869}
		\end{center}
	\end{figure}

	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/13692.jpg}
		% Create a subtitle for the figure.
		\caption{result with three person}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13692}
		\end{center}
	\end{figure}

	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/img_13692.jpg}
		% Create a subtitle for the figure.
		\caption{three person in a photo}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13692_raw}
		\end{center}
	\end{figure}
	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/img_13869.jpg}
		% Create a subtitle for the figure.
		\caption{two person in a photo}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13869_raw}
		\end{center}
	\end{figure}

>>>>

\HRule \\[1cm]
{ \huge \bfseries The Experiment II Report of \textit{Machine Learning} }\\[0.6cm] % Title of your document
\HRule \\[2cm]
%----------------------------------------------------------------------------------------
%	HEADING SECTIONS
%----------------------------------------------------------------------------------------

@@

% Define document title and author
	\title{English-Chinese Translation Machine Based on Sequence to Sequence Network}
	\author{Jianqiao Hu \thanks{autor's email: 202221045886@mail.scut.edu.cn}}
	\maketitle

@@

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{L}{anguages} are carriers of information transmission. Many kinds of languages are being using among whole world. One of research target in natural language processing field is how translate a language into another language accurately. With the inspiration from classic sequence-to-sequence machine translation models like \cite{1703.01619} and attention mechanism added machine learning language translation models like. \cite{1706.03762}.

% Main Part
\section{Methods and Theory}
In \cite{8080244}, it propose Multi-task convolutional neural network to detect faces from images. Our experience used this method.

\section{Experiments}
\subsection{Dataset}
In this experience, we used English-Chinese translation dataset to train the model.

@@
